---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "100%",
  collapse = TRUE,
  comment = "#>"
)
```

# rucoin

An R API to KuCoin Crytocurrency market data and market orders.

**Currently only have supports for getting market data, and still in heavy development stage!**

## Installation

You can install the development version of `rucoin` using:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("bagasbgy/rucoin")
```

## Getting Started

First of all, let's start by importing the library:

```{r}
# import library
library(rucoin)
```

### Historical Data

For getting historical data, you can use `get_kucoin_prices()`:

```{r}
# get one pair of symbol prices
prices <- get_kucoin_prices(
  symbols = "BTC/USDT",
  from = "2019-06-01 00:00:00",
  to = "2019-06-02 00:00:00",
  frequency = "1 hour"
)

# quick check
prices
```

The `get_kucoin_prices()` function also support for querying multiple symbols:

```{r}
# get one pair of symbol prices
prices <- get_kucoin_prices(
  symbols = c("KCS/USDT", "BTC/USDT", "KCS/BTC"),
  from = "2019-06-01 00:00:00",
  to = "2019-06-02 00:00:00",
  frequency = "1 hour"
)

# quick check
prices
```

## Further Development

* API for market meta data
* API for market orders
